### 2019-08-06 README.Rmd
updated talking points after meeting

- Have you heard of trelliscope: https://hafen.github.io/trelliscopejs/#trelliscope
- I think I may have convinced Adam to talk at graphics group if we end up scheduling graphics group on Thursday
- opinions on saving pdf files to github - if no - what to do?
- adding a random noise variable to the model to see if LIME ever chooses it as an important variable
- can I remove some of the sources from the references file that I am not going to use?
- have you heard of: Journal of Data Science, Statistics, and Visualisation (jdssv.org)

@@

- draft background section
- read through papers giving an overview of the current explanation methods
- create first draft of JSM poster

>>>>

- Can I remove some of the sources from the references file that I am not going to use?

@@

- work on first draft of paper
- read through papers giving an overview of the current explanation methods
